---
title: "Jiaxing_accessibility"
author: "Yuanzhao Wang"
date: "11/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
options(java.parameters = "-Xmx4G")
```

Load libraries

```{r setup, message=FALSE}
library(r5r)
library(tidyverse)
library(sf)
library(irr)
library(ggthemes)
```


Load spatial datasets and add ID columns

```{r dataset, message=FALSE, warning=FALSE, results='hide'}
boundary <- st_read("Largefiles/ad_boundary/boundary.shp")

school <- st_read("Largefiles/school/school.shp") %>% 
  st_transform("WGS84") 

hospital <- st_read("Largefiles/hospitals/Jiaxing_hos.shp") %>% 
  st_transform("WGS84")

busstop <- st_read("Largefiles/busstop/Jiaxing_busstop.shp") %>% 
  st_transform("WGS84")

restaurant <- st_read("Largefiles/restaurants/Jiaxing_res.shp") %>% 
  st_transform("WGS84")
  
greenspace <- st_read("Largefiles/greenspace/greenspace.shp") %>% 
  st_transform("WGS84")

leis <- st_read("Largefiles/leisure/yule.shp") %>% 
  st_transform("WGS84")

public <- st_read("Largefiles/public_service/shenghuo.shp") %>% 
  st_transform("WGS84")
  
shopping <- st_read("Largefiles/shopping/shopping.shp")
  
weibo <- st_read("Largefiles/weibo_sa/weibo_sa.shp")

hospital$Id <- NULL
restaurant$Id <- NULL
  
school <- school %>%
    mutate(id = seq(1, length(school$Name)))
restaurant <- restaurant %>%
    mutate(id = seq(1, length(restaurant$geometry)))
greenspace <- greenspace %>%
    mutate(id = seq(1, length(greenspace$Name)))
hospital <- hospital %>%
    mutate(id = seq(1, length(hospital$geometry)))
weibo <- weibo %>%
    mutate(id = seq(1, length(weibo$geometry)))
shopping <- shopping %>%
    mutate(id = seq(1, length(shopping$geometry)))
public <- public %>%
    mutate(id = seq(1, length(public$geometry)))
leis <- leis %>%
    mutate(id = seq(1, length(leis$geometry)))
```

Plot street network with hospital locations 

```{r, message=FALSE, warning=FALSE, results='hide'}
jiaxing_streets <- st_read("jiaxing/osmdata_network_01.pbf", layer = "lines", quiet=TRUE)
greenspace_points <- st_centroid(greenspace)

ggplot(jiaxing_streets) +
  geom_sf() +
  geom_sf(data = hospital, color = "red") +
  theme_void()
```

Clip street network and layer of Weibo posts to city boundary

```{r CLIP, echo=FALSE}
jiaxing_streets <- jiaxing_streets[boundary,]
weibo_clip <- weibo[boundary,]
```

Create grid

```{r build grid, echo=FALSE}
grid <- st_sf(st_make_grid(boundary, square = FALSE,
                           n = c(100, 100),
                           what = "polygons")) %>% 
  st_filter(boundary)

colnames(grid) <- "geometry"
st_geometry(grid) <- "geometry"

grid <- grid %>% 
  mutate(id = seq(1, length(grid$geometry), by = 1))


ggplot() +
  geom_sf(data = grid)+
  theme_map()

grid_points <- st_centroid(grid)
ggplot() +
  geom_sf(data = grid_points, size = 0.75) +
  geom_sf(data = weibo_clip, color = "red") +
  theme_map()
```

get number of each type of destination in each grid cell

```{r}
grid <- grid %>%
  mutate(num_restaurant = lengths(st_covers(grid, restaurant))) %>%
  mutate(num_school = lengths(st_covers(grid, school)))%>%
  mutate(num_hospital = lengths(st_covers(grid, hospital)))%>%
  mutate(num_busstop = lengths(st_covers(grid, busstop)))%>%
  mutate(num_greenspace = lengths(st_covers(grid, greenspace_points)))%>%
  mutate(num_leis = lengths(st_covers(grid, leis)))%>%
  mutate(num_public = lengths(st_covers(grid, public)))%>%
  mutate(num_shopping = lengths(st_covers(grid, shopping)))

grid_points <- st_centroid(grid)

```


# run r5r

```{r, message=FALSE}
r5r_core <- setup_r5("jiaxing", verbose = FALSE)

```

# accessibility from weibo posted to nearest restaurant

```{r, message=FALSE, results='hide'}
restaurant_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_restaurant",
                                   mode = "WALK",
                                   decay_function = "logistic",
                                   cutoffs = 15,
                                   verbose = FALSE) %>%
  rename("restaurant_access" = "accessibility") %>%
  mutate(id = as.numeric(from_id)) %>%
  select("id", "restaurant_access")
  

weibo_clip <- weibo_clip %>%
  left_join(restaurant_access)
```

```{r}
ggplot(weibo_clip) +
  geom_sf(aes(color = restaurant_access), size = 0.1) +
  scale_color_viridis_c() +
  theme_map()
```

```{r}
ggplot(weibo_clip) +
  geom_sf(aes(color = positive_p), size = 0.1) +
  scale_color_viridis_c() +
  theme_map()
```

```{r}
model <- lm(positive_p ~ restaurant_access, data = weibo_clip)

summary(model)
```

# accessibility from weibo posted to other ficilities

```{r, message=FALSE, results='hide'}
school_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_school",
                                   mode = "WALK",
                                   decay_function = "logistic",
                                   cutoffs = 15,
                                   verbose = FALSE) %>%
  rename("school_access" = "accessibility") %>%
  mutate(id = as.numeric(from_id)) %>%
  select("id", "school_access")
  

weibo_clip <- weibo_clip %>%
  left_join(school_access)

hospital_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_hospital",
                                   mode = "WALK",
                                   decay_function = "logistic",
                                   cutoffs = 15,
                                   verbose = FALSE) %>%
  rename("hospital_access" = "accessibility") %>%
  mutate(id = as.numeric(from_id)) %>%
  select("id", "hospital_access")
  

weibo_clip <- weibo_clip %>%
  left_join(hospital_access)

busstop_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_busstop",
                                   mode = "WALK",
                                   decay_function = "logistic",
                                   cutoffs = 15,
                                   verbose = FALSE) %>%
  rename("busstop_access" = "accessibility") %>%
  mutate(id = as.numeric(from_id)) %>%
  select("id", "busstop_access")
  

weibo_clip <- weibo_clip %>%
  left_join(busstop_access)

greenspace_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_greenspace",
                                   mode = "WALK",
                                   decay_function = "logistic",
                                   cutoffs = 15,
                                   verbose = FALSE) %>%
  rename("greenspace_access" = "accessibility") %>%
  mutate(id = as.numeric(from_id)) %>%
  select("id", "greenspace_access")
  

weibo_clip <- weibo_clip %>%
  left_join(greenspace_access)

leis_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_leis",
                                   mode = "WALK",
                                   decay_function = "logistic",
                                   cutoffs = 15,
                                   verbose = FALSE) %>%
  rename("leis_access" = "accessibility") %>%
  mutate(id = as.numeric(from_id)) %>%
  select("id", "leis_access")
  

weibo_clip <- weibo_clip %>%
  left_join(leis_access)

public_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_public",
                                   mode = "WALK",
                                   decay_function = "logistic",
                                   cutoffs = 15,
                                   verbose = FALSE) %>%
  rename("public_access" = "accessibility") %>%
  mutate(id = as.numeric(from_id)) %>%
  select("id", "public_access")
  

weibo_clip <- weibo_clip %>%
  left_join(public_access)

shopping_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_shopping",
                                   mode = "WALK",
                                   decay_function = "logistic",
                                   cutoffs = 15,
                                   verbose = FALSE) %>%
  rename("shopping_access" = "accessibility") %>%
  mutate(id = as.numeric(from_id)) %>%
  select("id", "shopping_access")
  

weibo_clip <- weibo_clip %>%
  left_join(shopping_access)
```
```{r}
full_model <- lm(positive_p ~ restaurant_access + school_access + hospital_access + busstop_access + greenspace_access + leis_access + public_access + shopping_access, data = weibo_clip)

summary(full_model)
```
# ```{r}
# weibo_clip <- weibo_clip %>%
#  mutate(log_greenspace = log(greenspace_access), base = 2)
# 
# full_model2 <- lm(positive_p ~ restaurant_access + school_access + hospital_access + busstop_access + log_greenspace + leis_access + public_access + shopping_access, data = weibo_clip)
# 
# summary(full_model2)
# ```

# Inter-rater reliability
```{r read csv, message=FALSE, warning=FALSE, results='hide'}
reliability <- read_csv("reliability_test.csv")
```

# IPercentage agreement
```{r, message=FALSE, warning=FALSE, results='hide'}
ratings <- reliability %>% select(lei, YZ, TW)
agree(ratings)
```
```{r, message=FALSE, warning=FALSE, results='hide'}
ratings_ai <- reliability %>% select(AI, lei)
kappa2(ratings_ai)
```
