---
title: "Jiaxing_accessibility"
author: "Yuanzhao Wang"
date: "11/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
options(java.parameters = "-Xmx4G")
```

Load libraries

```{r setup, message=FALSE}
library(r5r)
library(tidyverse)
library(sf)
library(irr)
library(ggthemes)
library(jtools)
```


Load spatial datasets and add ID columns

```{r dataset, message=FALSE, warning=FALSE, results='hide'}
boundary <- st_read("Largefiles/ad_boundary/boundary.shp")

school <- st_read("Largefiles/school/school.shp") %>% 
  st_transform("WGS84") 

hospital <- st_read("Largefiles/hospitals/Jiaxing_hos.shp") %>% 
  st_transform("WGS84")

busstop <- st_read("Largefiles/busstop/Jiaxing_busstop.shp") %>% 
  st_transform("WGS84")

restaurant <- st_read("Largefiles/restaurants/Jiaxing_res.shp") %>% 
  st_transform("WGS84")
  
greenspace <- st_read("Largefiles/greenspace/greenspace.shp") %>% 
  st_transform("WGS84")

leis <- st_read("Largefiles/leisure/yule.shp") %>% 
  st_transform("WGS84")

public <- st_read("Largefiles/public_service/shenghuo.shp") %>% 
  st_transform("WGS84")
  
shopping <- st_read("Largefiles/shopping/shopping.shp")
  
weibo <- st_read("Largefiles/weibo_sa/weibo_sa.shp")

hospital$Id <- NULL
restaurant$Id <- NULL
  
school <- school %>%
    mutate(id = seq(1, length(school$Name)))
restaurant <- restaurant %>%
    mutate(id = seq(1, length(restaurant$geometry)))
greenspace <- greenspace %>%
    mutate(id = seq(1, length(greenspace$Name)))
hospital <- hospital %>%
    mutate(id = seq(1, length(hospital$geometry)))
weibo <- weibo %>%
    mutate(id = seq(1, length(weibo$geometry)))
shopping <- shopping %>%
    mutate(id = seq(1, length(shopping$geometry)))
public <- public %>%
    mutate(id = seq(1, length(public$geometry)))
leis <- leis %>%
    mutate(id = seq(1, length(leis$geometry)))
```

Plot street network with hospital locations 

```{r, message=FALSE, warning=FALSE, results='hide'}
jiaxing_streets <- st_read("jiaxing/osmdata_network_01.pbf", layer = "lines", quiet=TRUE)
greenspace_points <- st_centroid(greenspace)

ggplot(jiaxing_streets) +
  geom_sf() +
  geom_sf(data = hospital, color = "red") +
  theme_void()
```

Clip street network and layer of Weibo posts to city boundary

```{r CLIP, echo=FALSE}
jiaxing_streets <- jiaxing_streets[boundary,]
weibo_clip <- weibo[boundary,]
```

Create grid

```{r build grid, echo=FALSE}
grid <- st_sf(st_make_grid(boundary, square = FALSE,
                           n = c(100, 100),
                           what = "polygons")) %>% 
  st_filter(boundary)

colnames(grid) <- "geometry"
st_geometry(grid) <- "geometry"

grid <- grid %>% 
  mutate(id = seq(1, length(grid$geometry), by = 1))


ggplot() +
  geom_sf(data = grid)+
  theme_map()

grid_points <- st_centroid(grid)
ggplot() +
  geom_sf(data = grid_points, size = 0.75) +
  geom_sf(data = weibo_clip, color = "red") +
  theme_map()
```

get number of each type of destination in each grid cell

```{r}
grid <- grid %>%
  mutate(num_restaurant = lengths(st_covers(grid, restaurant))) %>%
  mutate(num_school = lengths(st_covers(grid, school)))%>%
  mutate(num_hospital = lengths(st_covers(grid, hospital)))%>%
  mutate(num_busstop = lengths(st_covers(grid, busstop)))%>%
  mutate(num_greenspace = lengths(st_covers(grid, greenspace_points)))%>%
  mutate(num_leis = lengths(st_covers(grid, leis)))%>%
  mutate(num_public = lengths(st_covers(grid, public)))%>%
  mutate(num_shopping = lengths(st_covers(grid, shopping)))

grid_points <- st_centroid(grid)

```


# run r5r

```{r, message=FALSE}
r5r_core <- setup_r5("jiaxing", verbose = FALSE)

```

# accessibility from weibo posted to nearest restaurant

This will add five columns to weibo_clip:

restaurant_access_5: The number of restaurants within a 5-minute walk.
restaurant_access_10: The number of restaurants within a 10-minute walk.
restaurant_access_15: The number of restaurants within a 15-minute walk.
restaurant_access_20: The number of restaurants within a 15-minute walk.
restaurant_access_25: The number of restaurants within a 15-minute walk.

`for (i in seq(5, 25, by = 5))` means you want to generate values for cutoffs that range from 5 to 25 minutes, increasing in increments of 5 minutes. You can get more columns by editing that line to get a wider range and/or increase by smaller increments.

```{r, message=FALSE, results='hide'}
for (i in seq(5, 25, by=5)) {
  restaurant_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_restaurant",
                                   mode = "WALK",
                                   decay_function = "step",
                                   cutoffs = i,
                                   verbose = FALSE) %>%
    mutate(id = as.numeric(from_id)) %>%
    select("id", "accessibility")

  colnames(restaurant_access) <- c("id",
                                   paste("restaurant_access_", i, sep = ""))

  weibo_clip <- weibo_clip %>%
    left_join(restaurant_access)
}
  


```

```{r}
ggplot(weibo_clip) +
  geom_sf(aes(color = restaurant_access_15), size = 0.1) +
  scale_color_viridis_c() +
  theme_map()
```

```{r}
ggplot(weibo_clip) +
  geom_sf(aes(color = positive_p), size = 0.1) +
  scale_color_viridis_c() +
  theme_map()
```

Now we can run the model for each of the threshold values and see which threshold gives the best model fit.

It looks like the 15-minute threshold gives the best model fit.

I recommend doing this individually for each of the amenities, and them use the variable that gives the best fit for each to combine into your final model.

```{r}
formula <- as.formula(paste("positive_p ~ restaurant_access_", 5, sep=""))
model <- lm(formula, data = weibo_clip)

fit <- tibble(threshold = 5,
              fit = summary(model)$r.squared)

for (i in seq(10, 25, by=5)) {
  formula <- as.formula(paste("positive_p ~ restaurant_access_", i, sep=""))
  model <- lm(formula, data = weibo_clip)

fit <- rbind(fit, c(i, summary(model)$r.squared))

  
}
fit

ggplot(fit, aes(x = threshold, y = fit)) +
  geom_point() +
  theme_bw()
```
# accessibility from weibo posted to greenspace

```{r, message=FALSE, results='hide'}
for (i in seq(5, 60, by=5)) {
  greenspace_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_greenspace",
                                   mode = "WALK",
                                   decay_function = "step",
                                   cutoffs = i,
                                   verbose = FALSE) %>%
    mutate(id = as.numeric(from_id)) %>%
    select("id", "accessibility")

  colnames(greenspace_access) <- c("id",
                                   paste("greenspace_access_", i, sep = ""))

  weibo_clip <- weibo_clip %>%
    left_join(greenspace_access)
}
  


```

```{r}
formula <- as.formula(paste("positive_p ~ greenspace_access_", 5, sep=""))
model <- lm(formula, data = weibo_clip)

fit <- tibble(threshold = 5,
              fit = summary(model)$r.squared)

for (i in seq(10, 60, by=5)) {
  formula <- as.formula(paste("positive_p ~ greenspace_access_", i, sep=""))
  model <- lm(formula, data = weibo_clip)

fit <- rbind(fit, c(i, summary(model)$r.squared))

  
}
fit

ggplot(fit, aes(x = threshold, y = fit)) +
  geom_point() +
  theme_bw()
```
# accessibility from weibo posted to school

```{r, message=FALSE, results='hide'}
for (i in seq(5, 30, by=5)) {
  school_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_school",
                                   mode = "WALK",
                                   decay_function = "step",
                                   cutoffs = i,
                                   verbose = FALSE) %>%
    mutate(id = as.numeric(from_id)) %>%
    select("id", "accessibility")

  colnames(school_access) <- c("id",
                                   paste("school_access_", i, sep = ""))

  weibo_clip <- weibo_clip %>%
    left_join(school_access)
}
  
formula <- as.formula(paste("positive_p ~ school_access_", 5, sep=""))
model <- lm(formula, data = weibo_clip)

fit <- tibble(threshold = 5,
              fit = summary(model)$r.squared)

for (i in seq(10, 30, by=5)) {
  formula <- as.formula(paste("positive_p ~ school_access_", i, sep=""))
  model <- lm(formula, data = weibo_clip)

fit <- rbind(fit, c(i, summary(model)$r.squared))

  
}
fit

ggplot(fit, aes(x = threshold, y = fit)) +
  geom_point() +
  theme_bw()

```

# accessibility from weibo posted to hospital

```{r, message=FALSE, results='hide'}
for (i in seq(5, 30, by=5)) {
  hospital_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_hospital",
                                   mode = "WALK",
                                   decay_function = "step",
                                   cutoffs = i,
                                   verbose = FALSE) %>%
    mutate(id = as.numeric(from_id)) %>%
    select("id", "accessibility")

  colnames(hospital_access) <- c("id",
                                   paste("hospital_access_", i, sep = ""))

  weibo_clip <- weibo_clip %>%
    left_join(hospital_access)
}
  
formula <- as.formula(paste("positive_p ~ hospital_access_", 5, sep=""))
model <- lm(formula, data = weibo_clip)

fit <- tibble(threshold = 5,
              fit = summary(model)$r.squared)

for (i in seq(10, 30, by=5)) {
  formula <- as.formula(paste("positive_p ~ hospital_access_", i, sep=""))
  model <- lm(formula, data = weibo_clip)

fit <- rbind(fit, c(i, summary(model)$r.squared))

  
}
fit

ggplot(fit, aes(x = threshold, y = fit)) +
  geom_point() +
  theme_bw()

```
# accessibility from weibo posted to busstop

```{r, message=FALSE, results='hide'}
for (i in seq(5, 90, by=5)) {
  busstop_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_busstop",
                                   mode = "WALK",
                                   decay_function = "step",
                                   cutoffs = i,
                                   verbose = FALSE) %>%
    mutate(id = as.numeric(from_id)) %>%
    select("id", "accessibility")

  colnames(busstop_access) <- c("id",
                                   paste("busstop_access_", i, sep = ""))

  weibo_clip <- weibo_clip %>%
    left_join(busstop_access)
}
  
formula <- as.formula(paste("positive_p ~ busstop_access_", 5, sep=""))
model <- lm(formula, data = weibo_clip)

fit <- tibble(threshold = 5,
              fit = summary(model)$r.squared)

for (i in seq(10, 90, by=5)) {
  formula <- as.formula(paste("positive_p ~ busstop_access_", i, sep=""))
  model <- lm(formula, data = weibo_clip)

fit <- rbind(fit, c(i, summary(model)$r.squared))

  
}
fit

ggplot(fit, aes(x = threshold, y = fit)) +
  geom_point() +
  theme_bw()

```
# accessibility from weibo posted to leis

```{r, message=FALSE, results='hide'}
for (i in seq(5, 30, by=5)) {
  leis_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_leis",
                                   mode = "WALK",
                                   decay_function = "step",
                                   cutoffs = i,
                                   verbose = FALSE) %>%
    mutate(id = as.numeric(from_id)) %>%
    select("id", "accessibility")

  colnames(leis_access) <- c("id",
                                   paste("leis_access_", i, sep = ""))

  weibo_clip <- weibo_clip %>%
    left_join(leis_access)
}
  
formula <- as.formula(paste("positive_p ~ leis_access_", 5, sep=""))
model <- lm(formula, data = weibo_clip)

fit <- tibble(threshold = 5,
              fit = summary(model)$r.squared)

for (i in seq(10, 30, by=5)) {
  formula <- as.formula(paste("positive_p ~ leis_access_", i, sep=""))
  model <- lm(formula, data = weibo_clip)

fit <- rbind(fit, c(i, summary(model)$r.squared))

  
}
fit

ggplot(fit, aes(x = threshold, y = fit)) +
  geom_point() +
  theme_bw()

```
# accessibility from weibo posted to public

```{r, message=FALSE, results='hide'}
for (i in seq(5, 30, by=5)) {
  public_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_public",
                                   mode = "WALK",
                                   decay_function = "step",
                                   cutoffs = i,
                                   verbose = FALSE) %>%
    mutate(id = as.numeric(from_id)) %>%
    select("id", "accessibility")

  colnames(public_access) <- c("id",
                                   paste("public_access_", i, sep = ""))

  weibo_clip <- weibo_clip %>%
    left_join(public_access)
}
  
formula <- as.formula(paste("positive_p ~ public_access_", 5, sep=""))
model <- lm(formula, data = weibo_clip)

fit <- tibble(threshold = 5,
              fit = summary(model)$r.squared)

for (i in seq(10, 30, by=5)) {
  formula <- as.formula(paste("positive_p ~ public_access_", i, sep=""))
  model <- lm(formula, data = weibo_clip)

fit <- rbind(fit, c(i, summary(model)$r.squared))

  
}
fit

ggplot(fit, aes(x = threshold, y = fit)) +
  geom_point() +
  theme_bw()

```
# accessibility from weibo posted to shopping

```{r, message=FALSE, results='hide'}
for (i in seq(5, 30, by=5)) {
  shopping_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_shopping",
                                   mode = "WALK",
                                   decay_function = "step",
                                   cutoffs = i,
                                   verbose = FALSE) %>%
    mutate(id = as.numeric(from_id)) %>%
    select("id", "accessibility")

  colnames(shopping_access) <- c("id",
                                   paste("shopping_access_", i, sep = ""))

  weibo_clip <- weibo_clip %>%
    left_join(shopping_access)
}
  
formula <- as.formula(paste("positive_p ~ shopping_access_", 5, sep=""))
model <- lm(formula, data = weibo_clip)

fit <- tibble(threshold = 5,
              fit = summary(model)$r.squared)

for (i in seq(10, 30, by=5)) {
  formula <- as.formula(paste("positive_p ~ shopping_access_", i, sep=""))
  model <- lm(formula, data = weibo_clip)

fit <- rbind(fit, c(i, summary(model)$r.squared))

  
}
fit

ggplot(fit, aes(x = threshold, y = fit)) +
  geom_point() +
  theme_bw()

```

```{r}

full1_model <- lm(positive_p ~ restaurant_access_15 + school_access_15 + hospital_access_15 + busstop_access_15 + greenspace_access_15 + leis_access_15 + public_access_15 + shopping_access_15, data = weibo_clip)

summary(full1_model)


full2_model <- lm(positive_p ~ restaurant_access_15 + school_access_25 + hospital_access_25 + busstop_access_70 + greenspace_access_25 + leis_access_20 + public_access_15 + shopping_access_25, data = weibo_clip)

summary(full2_model)

coeff_names <- c("Costant" = "(Intercept)")

export_summs(full1_model, full2_model,
             error_format = "(p = {p.value})",
             error_pos = "same",
             model.name = c ("Initial",
                             "Refined"),
             coef=coeff_names)
```
# ```{r}
# weibo_clip <- weibo_clip %>%
#  mutate(log_greenspace = log(greenspace_access), base = 2)
# 
# full_model2 <- lm(positive_p ~ restaurant_access + school_access + hospital_access + busstop_access + log_greenspace + leis_access + public_access + shopping_access, data = weibo_clip)
# 
# summary(full_model2)
# ```

# Inter-rater reliability
```{r read csv, message=FALSE, warning=FALSE, results='hide'}
reliability <- read_csv("reliability_test.csv")
```

# IPercentage agreement
```{r, message=FALSE, warning=FALSE, results='hide'}
ratings <- reliability %>% select(lei, YZ, TW)
agree(ratings)
```
```{r, message=FALSE, warning=FALSE, results='hide'}
ratings_ai <- reliability %>% select(AI, lei)
kappa2(ratings_ai)
```
